---
title: "R Notebook- understand and check xcp fcon output for schaefer parcellation
output: html_notebook
---


```{r}
# clear variables
rm(list=ls(all=TRUE))
```


```{r warning=FALSE}
library(plyr)
library(tidyr)
library(dplyr)
library(purrr)
```


```{r}
schaefer_lut <- read.table("./xcp_output-fcon/Schaefer2018_400Parcels_17Networks_order.txt",header=FALSE)
schaefer_lut <- schaefer_lut[,1:2]
names(schaefer_lut) <- c("roi_index","roi_label")
schaefer_lut$roi_label = gsub(pattern = "17Networks_", replacement = "", x = schaefer_lut$roi_label)  
```


Functional connectivity files of interest
* prefix_{atlas_name}_network.txt # correlation matrix in vector form
* prefix_{atlas_name}.net # Pajek adjacency matrix
* prefix_{atlas_name}_ts.1D # Nodal time series
* prefix_{atlas_name}.nii.gz # atlas in input BOLD signal space

Load to have a look:
```{r}
# subject 202
sub_correlation_matrix_vector <- read.table("./xcp_output-fcon/sub-BIKE202/fcon/schaefer400/sub-BIKE202_schaefer400_network.txt",header=FALSE)

sub_correlation_matrix_net <- read.table("./xcp_output-fcon/sub-BIKE202/fcon/schaefer400/sub-BIKE202_schaefer400.net",header=FALSE,sep=" ",skip=2)
sub_correlation_matrix_net <- sub_correlation_matrix_net[,1:3]
names(sub_correlation_matrix_net) <- c("roi1","roi2","fc")
```

look-up table example
http://best-answer.net/easy-way-to-perform-a-lookup-in-r/

```{r}
sub_correlation_matrix_net$roi1_name <- schaefer_lut[match(sub_correlation_matrix_net$roi1,schaefer_lut$roi_index),"roi_label"]
sub_correlation_matrix_net$roi2_name <- schaefer_lut[match(sub_correlation_matrix_net$roi2,schaefer_lut$roi_index),"roi_label"]
```



great start!
-consider separating roi labels by informative pieces for grouping
-use dplyr to group_by and summarize
-consider how to run across subjects