---

title:"R Notebook understand and check xcp fcon output for schaefer parcellation
output:html_notebook

---


```{r}
# clear variables
rm(list=ls(all=TRUE))
```


```{r warning=FALSE}
library(plyr)
library(tidyr)
library(dplyr)
library(purrr)
```


```{r}
schaefer_lut <- read.table("./xcp_output-fcon/Schaefer2018_400Parcels_17Networks_order.txt",header=FALSE)
schaefer_lut <- schaefer_lut[,1:2]
names(schaefer_lut) <- c("roi_index","roi_label")
schaefer_lut$roi_label = gsub(pattern = "17Networks_", replacement = "", x = schaefer_lut$roi_label)  
```


Functional connectivity files of interest
* prefix_{atlas_name}_network.txt # correlation matrix in vector form
* prefix_{atlas_name}.net # Pajek adjacency matrix
* prefix_{atlas_name}_ts.1D # Nodal time series
* prefix_{atlas_name}.nii.gz # atlas in input BOLD signal space


```{r}

# load sublist
subs <- read.table("fcon_sublist.txt",header=FALSE)
names(subs) <- c("subject_id")

# look in all files that match pattern 
files <- dir(pattern="sub-.*\\_schaefer400\\.net", all.files = T, recursive=T)

# create empty data frame to fill with subject data
fcon_df <- data.frame()

# for each subject in list, find+load+reformat variable names, concatenate all subjects with rbind
for (i in subs$subject_id){
     print(i)
        subject_id <- i
        match <- grepl(x=files, pattern=i)
        whichfile <- files[match]
        sub_correlation_matrix_net <- read.table(whichfile,header=FALSE,sep=" ",skip=2)
        sub_correlation_matrix_net <- sub_correlation_matrix_net[,1:3] 
        names(sub_correlation_matrix_net) <- c("roi1","roi2","fc") # give headers
        sub_correlation_matrix_net$subject_id <- i
        fcon_df <<- rbind(fcon_df,sub_correlation_matrix_net)
}

```

match roi index with label

look-up table example
http://best-answer.net/easy-way-to-perform-a-lookup-in-r/

```{r}
fcon_df$roi1_name <- schaefer_lut[match(fcon_df$roi1,schaefer_lut$roi_index),"roi_label"]
fcon_df$roi2_name <- schaefer_lut[match(fcon_df$roi2,schaefer_lut$roi_index),"roi_label"]
```


```{r}
fcon_df <- fcon_df %>%
separate(col= roi1_name, sep="_", into = c("roi1_hemi", "roi1_subnetwork", "roi1_region", "roi1_regionindex"))

fcon_df <- fcon_df %>%
separate(col= roi2_name, sep="_", into = c("roi2_hemi", "roi2_subnetwork", "roi2_region", "roi2_regionindex"))
```


```{r}
# fix the region index and label mapping to their correct columns
fcon_df$roi1_regionindex <- ifelse(is.na(fcon_df$roi1_regionindex),fcon_df$roi1_region,fcon_df$roi1_regionindex)
fcon_df$roi1_region <- ifelse(fcon_df$roi1_region==fcon_df$roi1_regionindex," ",fcon_df$roi1_region)
fcon_df$roi2_regionindex <- ifelse(is.na(fcon_df$roi2_regionindex),fcon_df$roi2_region,fcon_df$roi2_regionindex)
fcon_df$roi2_region <- ifelse(fcon_df$roi2_region==fcon_df$roi2_regionindex," ",fcon_df$roi2_region)

```


for each roi pair, give network relation a within and between label 
```{r}
fcon_df$net_relation <- ifelse(fcon_df$roi1_subnetwork==fcon_df$roi2_subnetwork,"within","between")
```

for each roi pair, give hemisphere label for within or between
```{r}
fcon_df$hemi_relation <- ifelse(fcon_df$roi1_hemi==fcon_df$roi2_hemi,"within","between")
```



averages for within, group_by subnetwork
```{r}
subnet_avgs <- fcon_df %>%
        select(subject_id,roi1_subnetwork,roi1_hemi,roi2_subnetwork,roi2_hemi,fc,net_relation,hemi_relation) %>%
        filter(net_relation=="within",hemi_relation=="within") %>%
        group_by(subject_id,roi1_subnetwork,roi1_hemi) %>% 
        rename(subnetwork = roi1_subnetwork) %>% 
        rename(hemi = roi1_hemi) %>% 
        summarize(avgfc = mean(fc))

head(subnet_avgs)      
tail(subnet_avgs)     
```


Keeping in long-form often helpful for plotting and later stats
```{r}

library(ggplot2)

# center title
theme_update(plot.title = element_text(hjust = 0.5))

# making a bar plot with side-by-side bars for a factor
ggplot(data = subnet_avgs, aes(x = subnetwork, y = avgfc, fill=hemi)) +
        stat_summary(aes(y = avgfc), size=.5, fun.y = mean, geom="bar",size=1, position="dodge") + 
        stat_summary(fun.data=mean_se, geom="pointrange", size=.5, position=position_dodge(1)) + 
        scale_colour_manual(values=c("#3366CC","#339900")) +
        labs(title="Average rsFC") +
        scale_x_discrete(name="subnetwork") + 
        scale_y_continuous(name = "Functional Connectivity") +
        theme(title=element_text(size=20, face='bold'),
        axis.text.x = element_text(size=10,face='bold',angle = 30, hjust = 1),
        axis.text.y = element_text(size=15,face='bold'),
        axis.title.y = element_text(size=15))

# save last made plot, many extensions possible
ggsave(filename="subnet_avgs-schaefer-400_dsn-acompcor.png",width=300,height=200,units=c("mm"),dpi=300)

```


Write out averages to csv for use in additional individual differences analyses (for another notebook)

```{r}
write.csv(subnet_avgs,"subnet_avgs-schaefer-400_dsn-acompcor.csv",row.names=FALSE)
```

